Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-18 why-negative-selection.Rmd
move inequality table to _drake

drake::loadd(age_qual_weights)

ineq <- famhist %>% 
          left_join(age_qual_weights, by = "f.eid") %>% 
          filter(! is.na(n_children), ! is.na(income_cat), ! is.na(weights)) %>% 
          group_by(income_cat) %>% 
          summarize(across(all_of(score_names), 
                    list(
                      unw = ~ weighted.mean(.x, weights, na.rm = TRUE),
                      wtd = ~ weighted.mean(.x, weights * n_children, 
                                              na.rm = TRUE)
                    )
          )) %>% 
          tidyr::pivot_longer(-income_cat, 
                                names_to = c("score", ".value"), 
                                names_pattern = "(.*)_(.+?)$"
                              )

ineq_comp <-  left_join(
                ineq %>% filter(income_cat == 1),
                ineq %>% filter(income_cat == 5),
                by = "score"
              )

>>>>

drake::loadd(res_ineq)

ineq_comp <-  left_join(
                res_ineq %>% filter(income_cat == 1),
                res_ineq %>% filter(income_cat == 5),
                by = "score"
              )
